\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[margin=1in]{geometry}
\begin{document}

\section*{Caravan Pricing and Opportunity Model}

\paragraph{Notation.}
Items $i \in \mathcal{I}$, countries/towns $c \in \mathcal{C}$, origin $o$, destination $d$, time index $t$.
Let $S_{i,t}(c)$ and $D_{i,t}(c)$ denote supply and demand; $T(o,d)$ travel time (days);
$R(o\!\to\! d)$ a unitless route risk (0--1 or scaled); and $\varepsilon>0$ a small constant.
Let $f_\theta(\cdot)$ be the learned price model (linear, ridge, or ensemble).

\subsection*{Baseline Prediction}
A feature vector $\mathbf{x}_{i,t}(c)$ encodes distance centralities, recent volatility, local production focus,
neighbor prices, and other engineered signals. The baseline (data-driven) price is
\begin{equation}
\hat P_{i,t}(c) \;=\; f_\theta\!\big(\mathbf{x}_{i,t}(c)\big).
\end{equation}

\subsection*{Structural Adjustments}
Supply/demand imbalance and exogenous events apply multiplicative adjustments:
\begin{align}
A_{i,t}(c) &= 1 \;+\; \alpha \,\frac{D_{i,t}(c)-S_{i,t}(c)}{S_{i,t}(c)+\varepsilon}, \\[4pt]
M^{\mathrm{event}}_{i,t}(c) &\in \mathbb{R}_{>0}.
\end{align}
Define the effective local price:
\begin{equation}
P^{\mathrm{eff}}_{i,t}(c) \;=\; \hat P_{i,t}(c)\,A_{i,t}(c)\,M^{\mathrm{event}}_{i,t}(c).
\end{equation}

\subsection*{Route Costs and Reputation/Tariffs}
Travel introduces a landed-cost term and a bilateral multiplier for reputation/tariffs:
\begin{align}
L_{i,t}(o\!\to\! d) &= \kappa\,T(o,d) \;+\; \rho\,R(o\!\to\! d), \\[4pt]
M^{\mathrm{rep}}_{i,t}(o\!\to\! d) &= 1 \;+\; \tau_{i,t}(o\!\to\! d),
\end{align}
where $\kappa$ is per-day cost and $\rho$ weights risk; $\tau$ captures taxes, penalties, or discounts based on bilateral relations and item type.

\subsection*{Destination Ask and Opportunity}
When selling item $i$ in $d$ sourced from $o$, the adjusted destination ask is
\begin{equation}
\tilde P_{i,t}(d \mid o) \;=\; P^{\mathrm{eff}}_{i,t}(d)\,M^{\mathrm{rep}}_{i,t}(o\!\to\! d) \;+\; L_{i,t}(o\!\to\! d).
\end{equation}
Compute the opportunity ratio and margin:
\begin{align}
\mathcal{R}_{i,t}(o\!\to\! d) &= \frac{\tilde P_{i,t}(d \mid o)}{P^{\mathrm{eff}}_{i,t}(o)}, \\
\mathrm{Margin}(o\!\to\! d) &= \mathcal{R}_{i,t}(o\!\to\! d) - 1.
\end{align}
We consider trades where $\mathcal{R}_{i,t} > \gamma$ for threshold $\gamma$ (e.g., $1.15$).

\paragraph{Notes.} In implementation, feature scaling and model selection are tracked per-item type; volatility is computed over recent windows; and production focus can enter as a small additive term in $\tau$ to favor exporters or penalize import-strained goods.

\end{document}
